---
title       : A Signal-to-Noise Ratio (SNR) Visualization Utility
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

- This utility helps to get a sense of what a simple signal would look like at various signal-to-noise ratio (SNR) levels.

- SNR is defined as: $$SNR = 10*log10(\frac{Power Of Signal}{Power Of Noise})$$, in decibels (dB)

- Typically, in communications settings, the noise being added is Gaussian distributed

---

## Example Calculations

The power of the sine wave $Asin(wt)$ is $\frac{A^2}{2}$. To make things easy, just let $A=1$, then we say the power in our signal is $Ps = 0.5$.

If we add noise with equal power to the signal, then the SNR is a low value : $SNR=10*log10(\frac{0.5}{0.5}) = 0$.

If we add noise with much lower power than the signal, then the SNR will be a high value : $SNR=10*log10(\frac{0.5}{0.0005}) = 30$.

```{r, echo=FALSE}
Pn <- c(5, 0.5, 0.05, 0.0005, 0.00005)
Ps <- 0.5*rep(1,length(Pn))
snr <- 10*log10(Ps/Pn)
data <- data.frame(Ps.in.Watts=Ps, Pn.in.Watts=Pn, SNR.in.dB=snr)
knitr::kable(data, caption = "Example SNR Values")
```

But what does this actually *look* like?

---

## Example Plot

A low SNR makes the sine wave obscured, a high SNR makes the signal look very clean:

```{r, echo=FALSE, fig.width=12}
   library(ggplot2)

   N <- 15
   NT <- 10
   pi <- 3.14159

   snr <- 50
   varn <- 10^(-snr/20)/sqrt(2)

   x    <- sin(2*pi*c(0:((N*NT)-1))/N)
   noisy_x <- x + varn*rnorm(N*NT)

   df30 <- data.frame(SNR=30*rep(1,length(x)),x=c(0:((N*NT)-1)), y=noisy_x)

   snr <- -6
   varn <- 10^(-snr/20)/sqrt(2)

   x    <- sin(2*pi*c(0:((N*NT)-1))/N)
   noisy_x <- x + varn*rnorm(N*NT)

   dfm10 <- data.frame(SNR=-6*rep(1,length(x)),x=c(0:((N*NT)-1)), y=noisy_x)
                       
   df <- rbind(dfm10,df30)

   # draw the signal with the specified SNR
   ggplot(data=df, aes(x=x,y=y)) + 
      geom_point() +
      geom_line() + 
      theme_bw() + 
      labs(title="Two Very Different SNR Values", x="Sample Number", y="Voltage") +
      ylim(-6,6) +
      facet_grid(cols=vars(SNR))

```

---

## Run the Utility!!

You can play around with visualizing different levels of SNR with the utility at [this site](https://prog-bouillet.shinyapps.io/Coursera-JHSPH-DataProducts-FInalProject)


